Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-07 CAs_operads.tex
MAJ

Let us describe the normal forms for arity $n\geq 11$. For that, we 
consider the following "zig-zag" of degree $k \geq 0$ 
\Todo{Dessins}
\begin{equation}
  z_k :=.
\end{equation}
For instance, $z_3$ and $z_4$ are the following trees
\begin{equation}
.
\end{equation}
The normal forms are decomposed in two families. 
The first family is the set of the $n-1$ trees 
$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$, 
pictured as follows
\begin{equation}\label{equ:normal_forms_type_A}
   z_k \circ_{k+1} z_{n-1-k} = dessin.
\end{equation}
The second family is composed of the following four trees
\begin{equation}\label{equ:normal_forms_type_B}
  \RComb{n-1}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node(9)at(6,-6.75){};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](7)--(9);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node(1)at(1.00,-2.25){};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](1)--(3);
    \draw[Edge](7)--(9);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-3\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](7)--(9);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}.
\end{equation}
Indeed, each of these trees avoids the left membres of the convergent
presentation given in Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}.
Moreover, we have the following.
\medbreak

>>>>

Let us describe the normal forms for arity $n\geq 11$. For that, we 
consider the following "zig-zag" of degree $k \geq 0$ 
\Todo{Dessins}
\begin{equation}
  z_k :=.
\end{equation}
For instance, $z_3$ and $z_4$ are the following trees
\begin{equation}
.
\end{equation}
The normal forms are decomposed into two families. 
The first family is the set of the $n-1$ trees 
$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$, 
pictured as follows
\begin{equation}\label{equ:normal_forms_type_A}
   z_k \circ_{k+1} z_{n-1-k} = dessin.
\end{equation}
The second family is composed of the following four trees
\begin{equation}\label{equ:normal_forms_type_B}
  \RComb{n-1}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node(9)at(6,-6.75){};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](7)--(9);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node(1)at(1.00,-2.25){};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](1)--(3);
    \draw[Edge](7)--(9);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}, \qquad
  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
    \node(0)at(0.00,-4.50){};
    \node(2)at(2.00,-4.50){};
    \node(8)at(8.00,-6.75){};
    \node(10)at(5,-9){};
    \node(11)at(7,-9){};
    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-3\end{math}};
    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](7)--(9);
    \draw[Edge](9)--(10);
    \draw[Edge](9)--(11);
    \draw[Edge, dotted](7)--(3);
    \draw[Edge](8)--(7);
    \node(r)at(3.00,1.74){};
    \draw[Edge](r)--(3);
  \end{tikzpicture}.
\end{equation}
Indeed, each of these $n+3$ trees avoids the left membres of the
convergent presentation given in
Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}. Moreover, we have the
following.
\medbreak
